---
title: "MA615 Assignment 4 - Task Three"
author: "Yingjie Wang"
data: 2021/12/07
output:
  pdf_document:
    df_print: paged
---

```{r setup, include=FALSE}
options(warn=-1)
knitr::opts_chunk$set(echo = TRUE)

# install.packages("tidyverse")
# install.packages("sentimentr")
# install required packages

library(tidyverse)
library(gutenbergr)
library(sentimentr)
library(tidytext)
library(dplyr)
# import required packages

book_66790 <- gutenberg_download(66790) # download the book from gutenberg project
```

## Sentiment Analysis

I do try to load my book in test2 number space and fail. I found that I can only see the level 1 "anton/" rather than the level 2 "anton/hw_russian". And the code is in tnum-66790.R. 

So, I produce a sentence-level sentiment analysis using "sentimentr" package.

Sentimentr is also a lexicon-based package. One of the difference is that it can accurately capture the Valence Shifters like Negation that can flip the polarity of a sentence with one word. Like "Hungry" vs. "Not hungry".

By comparing the result of Task Two and Task Three, I firstly make their index consistent with each other, which means the whole book is cut into word level and sentence level separately, but then are both assigned to ~300 blocks. So we can directly compare the result of the both tasks at each index. They do have similarity, like [40-50], [180-220], [130-150]. There are also some reverse result (possibly due to Negation), like [220-240]..


```{r echo=FALSE, include=FALSE}
book_str <- paste(book_66790$text, sep = "")

book_sentiment <- book_str %>%
  get_sentences() %>%
  sentiment() %>%
  filter(!is.na(word_count)) %>%
  mutate(index = row_number() %/% 40, polarity_level = ifelse(sentiment < -0.2, "negative", ifelse(sentiment > 0.2, "positive", "neutral"))) %>%
  count(index, polarity_level) %>%
  spread(polarity_level, n, fill = 0) %>%
  mutate(polarity_level = positive - negative)
```

```{r echo=FALSE}
ggplot(book_sentiment, aes(index, polarity_level, fill = 66790)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~"Russian Silhouettes: More Stories of Russian Life", ncol = 1, scales = "free_x")
# Plot the sentiment analysis.
```

