---
title: "MA615 Assignment 4 - Task Two"
author: "Yingjie Wang"
data: 2021/12/07
output:
  pdf_document:
    df_print: paged
---

```{r setup, include=FALSE}
options(warn=-1)
knitr::opts_chunk$set(echo = TRUE)

# install.packages("gutenbergr")
# install.packages("dplyr")
# install.packages("tidytext")
# install required packages

library(gutenbergr)
library(dplyr)
library(stringr)
library(tidytext)
library(tidyr)
library(ggplot2) 
# import required packages

book <- gutenberg_download(66790) # download the book from the gutenberg project
```

## Sentiment Analysis

After conduct three lexicons, I select "bing" lexicon to conduct the word-level sentiment analysis.

1. The "Afinn" lexicon will return a numeric socre between -5 and 5

2. The "Bing" and "Nrc" lexicons will return a binary class (positive and negative)

Firstly, I indexes all the words in the order along the timeline of the book. Then, I cut them into several ~300 blocks. And I just count the number of positive words and number of negative words separately. Finally, use the difference as the level of sentiment and plot it. 

The data structure utilize to stored the text are list and tibble. 

And the statistic information like count is storead as a new column of tibble..


```{r echo=FALSE, include=FALSE}
tidy_book <- book %>%
  unnest_tokens(word, text) %>% # split the text into words
  anti_join(stop_words) %>% # remove stop words
  group_by(gutenberg_id) %>% 
  mutate(linenumber = row_number()) %>% # add a column of linenumber
  ungroup()

book_sentiment <- tidy_book %>%
  inner_join(get_sentiments("bing")) %>% # use "bing" lexicons
  count(gutenberg_id, index = linenumber %/% 100, sentiment) %>% # each batch contains 100 lines
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative) # use #positive_words - #negative_words as the level of sentiment
```


```{r echo=FALSE}
ggplot(book_sentiment, aes(index, sentiment, fill = gutenberg_id)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~"Russian Silhouettes: More Stories of Russian Life", ncol = 1, scales = "free_x")
# Plot the sentiment analysis.
```

